ODGI: scalable tools for pangenome graphs

### 2021-05-31 manuscript/main.tex
Edits

    \topic{odgi viz, sort, draw \& layout} pangenome visualization
    provides convenient insight into genomic variation (see
    Fig.~\ref{fig:1}). \cmd{odgi viz} generates a linearized
    representation of the pangenome and is capable of handling full
    length human chromosomes (Fig.~\ref{fig:1}a). \cmd{odgi sort}
    reorganises node order and simplifies the graph by applying
    several algorithms, including the novel `Path-Guided Stochastic Gradient Descent`
    algorithm. \cmd{odgi layout} and \cmd{odgi draw} bring the
    visualization in 2D. (Fig.~\ref{fig:1}b).

    \topic{odgi stats, bin, depth \& degree} pangenome statistics allow exploring genome complexity at different
    levels of abstraction. \cmd{odgi stats} returns the number of nodes, edges, paths, and graph length, while
    \cmd{odgi bin} summarizes the path information into bins of specified size, enabling a summarized view of
    gigabase scale graphs. \cmd{odgi depth} and \cmd{odgi degree} return the node depth and degree, respectively, as
    defined by query criteria, allowing users to detect complex regions due to sequences with highly identical
    repeats, or problems in the pangenome graph.

>>>>

    \topic{odgi viz, sort, draw \& layout} pangenome visualization
    provides convenient insight into genomic variation. \cmd{odgi viz}
    generates a linearized representation of the pangenome and is
    capable of handling full length human chromosomes
    (Fig.~\ref{fig:1}a). \cmd{odgi sort} reorganises node order and
    simplifies the graph by applying several algorithms, including the
    novel `Path-Guided Stochastic Gradient Descent' algorithm.
    \cmd{odgi layout} generates a file with the X-Y coordinates for
    all nodes and \cmd{odgi draw} draws the actual layout of the graph
    (Fig.~\ref{fig:1}b).

    \topic{odgi stats, bin, depth \& degree} pangenome numerical
    counts provide insight into genome complexity in other
    ways. E.g., \cmd{odgi stats} returns the number of nodes,
    edges, paths, and graph length. \cmd{odgi bin} summarizes path
    information into bins of a specified size, thereby enabling a
    summarized view of gigabase scale graphs. \cmd{odgi depth} and
    \cmd{odgi degree} return the node depth and degree as defined by
    user provided criteria. These methods allow detection of complex
    genomic regions.
